Illusion Game Validation (Study 1)

### 2022-08-05 study1.Rmd
update stim

>>>>

We generated stimuli with the difficulty levels spaced non-linearly depending on the best underlying model (i.e., with an exponential, square or cubic spacing if the best model was *log*, *square root* or *cube root*). For instance, a linear space of [0.1, 0.2, 0.3, 0.4] can be transformed to an exponential space of [[0.1       , 0.19207744, 0.29186238, 0.4       ]]
